### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@7ebad97c94abdd8e51790494ddfc38f9c4abf9d4 🚀

\hypertarget{the-metaweb-embeds-ecological-hypotheses-and-practices}{%
\section{The metaweb embeds ecological hypotheses and
practices}\label{the-metaweb-embeds-ecological-hypotheses-and-practices}}

@@

@@

>>>>

\hypertarget{an-illustration-of-metaweb-embedding}{%
\section{An illustration of metaweb
embedding}\label{an-illustration-of-metaweb-embedding}}

In this section, we illustrate the embedding of a collection of
bipartite networks collected by \textbf{REF}, using truncated Singular
Value Decomposition (t-SVD). The code to reproduce this example (as a
Jupyter notebook) is available as supplementary material. The resulting
(binary) metaweb \(\mathcal{M}\) has 2131 interactions between 206
parasites and 121 hosts (the same metaweb was used for the illustration
of interaction inference through deep learning in Strydom, Catchen, et
al., 2021), and its adjacency matrix has full rank (\emph{i.e.} it
represents a space with 121 dimensions). All analyses were done using
Julia (Bezanson et al., 2017) version 1.7.2, \emph{Makie.jl}
(\textbf{Danisch2021MakJl?}), and \emph{EcologicalNetworks.jl} (Poisot
et al., 2019).

\hypertarget{the-metaweb-embeds-both-ecological-hypotheses-and-practices}{%
\section{The metaweb embeds both ecological hypotheses and
practices}\label{the-metaweb-embeds-both-ecological-hypotheses-and-practices}}

@@

\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
65--98. \url{https://doi.org/10.1137/141000671}

@@

\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
Poisot, T., Belisle, Z., Hoebeke, L., Stock, M., \& Szefer, P. (2019).
EcologicalNetworks.jl - analysing ecological networks. \emph{Ecography}.
\url{https://doi.org/10.1111/ecog.04310}
